\LARGE \bf Influence of child-robot spacial arrangement in a learning by teaching task

### 2016-02-04 paper-Ro_Man-2016.tex
advances on descripton of measures and add photos

\usepackage[pdftex]{graphicx}
%\graphicspath{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper we present a study in which we test the influence of child-robot spatial arrangement on child's focus of attention, child's perception of robot's performance in the CoWriter learning by teaching activity.
In this activity the child teaches a Nao obot how to handwrite. 
In our study, we explore two spatial condition from Kendon's F formation, the side-by-side and the face-t-face formations.

We have 3 conditions following Kendon's F formation: 
\begin{itemize}
\item side by side
\item face to face
%\item in L shape
\end{itemize}

@@

@@

In this activity the child plays the role of a teacher.

Proxemics

@@

Kendon F Formation in HRI
\cite{huttenrauch2006investigating}

@@

Number of child
Expe settings
Condition within subject but with 
\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{./figures/s2s_photo.jpg}
\caption[Side by SIde Condition]{}
\caption{}
\label{fig:s2s_photo}
\end{figure}

\subsection{Reward Mechanism}
The table interface on which the child and the robot practice their handwriting contains also two buttons that allow the child to give positive (green thumb-up) or negative (red thumb-down) feeback to the robot's handwriting.

We noticed that children were expetcing the robot to react. 
Now that the usage of these buttons have been proven, we will consider for futur experimemnt to allow the robot to react. 
For instance, if the child gives a positive feedback when the robot is actually improving, the robot should display a positive emotion.
If he is given a positive feedback but doesnt not actually make any progree, he might express doubt to force the child to be more exigeant.

\subsection{With-me-ness}
\cite{lemaignan2016realtime}
Present it as a measure of synchrony,

@@

%\subsection{Questionnaire on likeability and Interrelationship}

@@

\section*{ACKNOWLEDGMENT}

@@

ref all cowriter paper + paper of sharma sur withmeness

>>>>

\usepackage[pdftex]{graphicx}

%\graphicspath{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper we present a study in which we test the influence of child-robot spatial arrangement on child's focus of attention, child's perception of robot's performance in the CoWriter learning by teaching activity.
In this activity the child teaches a Nao robot how to handwrite. 
In our study, we explore two spatial condition from Kendon's F formation, the side-by-side and the face-t-face formations.

We have 2 conditions following Kendon's F formation: 
\begin{itemize}
\item side by side
\item face to face
%\item in L shape
\end{itemize}

@@

Robots to enhance childhood education

@@

\cite{Matsuzoe2012} had a similar approach than learning by teaching with their Care Receiving Robot that was being taken cared off and taugh by a child with physical interaction.

Proxemics : explain how spatial arrangement could influence the interaction

@@

Kendon F Formation in HRI: explain how spatial arrangement had influences in the past

Spatial arrangement is also a social signal that tells about the relationship between the persons.

\cite{huttenrauch2006investigating}

@@

Number of child
Expe settings
Condition within subject but with 
\begin{figure}[t!]
    \centering
        \includegraphics[height=1.2in]{./figures/f2f_photo.png}
        \caption{Face to face spatial formation}
   ~
        \includegraphics[height=1.2in]{./figures/s2s_photo2.jpg}
        \caption{Side by Side spatial formation}
\end{figure}

\subsection{Reward Mechanism}
The table interface on which the child and the robot practice their handwriting contains also two buttons that allow the child to give positive (green thumb-up) or negative (red thumb-down) feedback to the robot's handwriting.

We noticed that children were expecting the robot to react. 
Now that the usage of these buttons have been proven, we will consider for future experiment to allow the robot to react. 
For instance, if the child gives a positive feedback when the robot is actually improving, the robot should display a positive emotion.
If he is given a positive feedback but doesn’t not actually make any progress, he might express doubt to force the child to be more exigent.

\subsection{With-me-ness}
The with-me-ness measure applied in HRI in \cite{lemaignan2016realtime}, helps to set specific targets during each state of the interaction and to determine rather the user is looking at one of these targets or not. 
The algorithm is based on the d-lib library that helps to estimate the head pose of the user using a video from webcam device for instance.

This measure allow us to see if the child is engage in the interaction and is looking at the tablet or the robot's head when he/she should.

For this experiment, the targets where: "the observer"(a teacher or a teacher assistant), "the selection tablet"(the tablet used to pick a word),

Present it as a measure of synchrony,

@@

\subsection{Reward Mechanism}

\subsection{With-me-ness}

@@

\section*{ACKNOWLEDGMENT}
This research was partially supported by the Funda\c{c}\~{a}o para a Ci\^{e}ncia
e a Tecnologia (FCT) with reference UID/CEC/ 50021/2013, and by the Swiss
National Science Foundation through the National Centre of Competence in
Research Robotics.

@@
